Model LF

### 2022-12-13 Power point test.Rmd
Commit

>>>>

## Elasticiteter

```{r}
pr_change_unemp_02=(unemp_02-unemp_bs2)/unemp_bs2
pr_change_komp_r_02b=(komp_r_02b-komp_r_bs2b)/komp_r_bs2b
pr_change_wage_ds_02b=(wage_ds_02b-wage_ds_bs2b)/wage_ds_bs2b

#Elasticity on wage
pr_change_wage_ds_02b/pr_change_komp_r_02b
#Elasticity on unemployment
pr_change_unemp_02/pr_change_komp_r_02
```

### 2022-12-13 max_dp endogen stød.Rmd
Commit

```{r}
plot(wage_ds_t_bs2, col= "green"); lines(wage_ds_t, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

>>>>

```{r}
plot(wage_ds_t_bs2, col= "green"); lines(wage_ds_t, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(max_dp_bs2, col= "green"); lines(max_dp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```
